\documentclass[journal,draftclsnofoot,onecolumn]{IEEEtran}

% *** PACKAGES ***
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{textcomp}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage{color}

\newcommand{\etal}{\textit{et~al.}}

\begin{document}

\title{Insert Title: Focused Ultrasound Modulation of BOLD Functional Connectivity}

\author{First~A. Author,~\IEEEmembership{Member,~IEEE}, Second~B. Author, and Third~C. Author%
\thanks{Manuscript received Month DD, YYYY; revised Month DD, YYYY; accepted Month DD, YYYY. Date of publication Month DD, YYYY; date of current version Month DD, YYYY. This work was supported by XYZ (grant number). (Corresponding author: First Author.)}%
\thanks{First Author and Second Author are with the Department of Biomedical Engineering, Example University, City, State ZIP, USA (e-mail: first.author@example.edu).}%
\thanks{Third Author is with the Department of Neurology, Example Medical Center, City, State ZIP, USA.}%
\thanks{Color versions of one or more of the figures in this article are available online at https://ieeexplore.ieee.org.}%
\thanks{Digital Object Identifier (DOI): 10.1109/TBME.XXXX.XXXXXXX}}

\markboth{IEEE Transactions on Biomedical Engineering,~Vol.~XX, No.~XX, Month~20XX}%
{Author \MakeLowercase{\textit{et al.}}: Insert Running Title}

\maketitle

\begin{abstract}
\input{sections/abstract}
\end{abstract}

\begin{IEEEkeywords}
\input{sections/keywords}
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}
\input{sections/introduction}

\section{Materials and Methods}
\label{sec:methods}
\input{sections/methods}

\section{Results}
\label{sec:results}
\input{sections/results}

\section{Discussion}
\label{sec:discussion}
\input{sections/discussion}

\section{Conclusion}
\label{sec:conclusion}
\input{sections/conclusion}

\section*{Acknowledgments}
\input{sections/acknowledgments}

\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

\appendices
\section{Extended Methods}
\label{sec:appendix}
\input{sections/appendix}

\section*{Data Availability}
The data that support the findings of this study will be made available from the corresponding author upon reasonable request, subject to institutional review board restrictions.

\section*{Code Availability}
The analysis code is available at \href{https://github.com/USERNAME/REPO}{https://github.com/USERNAME/REPO}.

\nocite{smith2020fus,doe2021bold}

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
